Activities

### 2025-11-25 activities.qmd
corrected links to slides (251125 GH)

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. 
Invited speaker: <a href="/assets/Mariana_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Mariana Nold</a>. 
Further speakers for TG2: <a href="/assets/20250902_Kammer.pdf" target="_blank" rel="noopener noreferrer">Michael Kammer</a>, 
<a href="/assets/Aliaksandr_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Aliaksandr Hubin</a>, 
<a href="/assets/2025-09 Roes Heinze.pdf" target="_blank" rel="noopener noreferrer">Georg Heinze</a>.

>>>>

* Invited session at the [ROeS 2025](https://roes2025.at/index.html) (Conference of the Austro-Swiss Region of the International Biometric Society) in Graz, A, 14-18 Sep 2025. Topic of the session: Contrasting Bayesian and frequentist model building for descriptive research questions - a paired-design experiment of STRATOS-TG2. 
Invited speaker: Mariana Nold <a href="/assets/Mariana_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Slides</a>. 
Further speakers for TG2: Michael Kammer <a href="/assets/20250902_Kammer.pdf" target="_blank" rel="noopener noreferrer">Slides</a>, Aliaksandr Hubin 
<a href="/assets/Aliaksandr_slides_Roes_2025.pdf" target="_blank" rel="noopener noreferrer">Slides</a>, 
Georg Heinze <a href="/assets/2025-09 Roes Heinze.pdf" target="_blank" rel="noopener noreferrer">Slides</a>.
